Binocular combination in the autonomic nervous system

### 2024-05-07 manuscript.Rmd
Revised modelling and data presentation

---
title: 'Binocular combination in the autonomic nervous system'
author: |
 | Federico G. Segala$^1$, Joel T. Martin$^1$, Annie Y. Morsi$^1$, Alex R. Wade$^{1,2}$ & Daniel H. Baker$^{1,2}$
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: true
  html_document: default
bibliography: references.bib
link-citations: yes
linkcolor: black
csl: elife.csl
header-includes:
- \usepackage{caption}
---

@@

processdata <- 3  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 56GB of storage)

@@

# cut off for data inclusion (Mahalanobis distance for complex data)
SDthresh <<- 3
nbootstraps <<- 1000

@@

# settings for sampler 
numSavedSteps <- 10000    # total number of MCMC steps
adaptSteps <- 1000  # Number of steps to "tune" the samplers
burnInSteps <- 2000 
thinSteps <- 10
nChains <- 16
ncores <- 8  # because of multi-threading, this is usually double the true number of physical cores, so we halve the number as Stan can only use physical cores
options(mc.cores=ncores)

@@

$^2$York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.

@@

  includedvalues <- array(0,dim=c(4,24,6,5))
  includedvalues2 <- array(0,dim=c(4,24,6,5))

@@

      temp <- tempmasksP[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmasksP[cond,level] <- mean(temp[i])
        cleanmasksPCI[1,cond,level] <- mbs$lowerCI
        cleanmasksPCI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmeansP2[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmeansP2[cond,level] <- mean(temp[i])
        cleanmeansP2CI[1,cond,level] <- mbs$lowerCI
        cleanmeansP2CI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmasksP2[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        includedvalues2[expt,i,cond,level] <- 1
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmasksP2[cond,level] <- mean(temp[i])
        cleanmasksP2CI[1,cond,level] <- mbs$lowerCI
        cleanmasksP2CI[2,cond,level] <- mbs$upperCI
      }
    }
  }

@@

  save(file=paste0(datadir,'included.RData'),list=c('includedvalues','includedvalues2'))

@@

CRFmodelstring = "
  data {
    int<lower=1> Nsubj ;
    int<lower=1> Ntotal ;
    real y[Ntotal] ;
    real x[Ntotal] ;
    real<lower=0> w[Ntotal] ;
    int<lower=1> c[Ntotal] ;
    int<lower=1> s[Ntotal] ;
  }
  parameters {
    real<lower=1> Z[Nsubj] ;
    real<lower=0> Rmax[Nsubj] ;
    real<lower=0> wt[Nsubj] ;
    real<lower=0> k[Nsubj] ;
    real<lower=0> p[Nsubj] ;    
    real<lower=0> q[Nsubj] ;    
    real<lower=0> sigma ;
    real<lower=1> Zmu ; 
    real<lower=0> Rmaxmu ; 
    real<lower=0> wtmu ; 
    real<lower=0> kmu ; 
    real<lower=0> pmu ;     
    real<lower=0> qmu ;     
    real<lower=0> Zsigma ;
    real<lower=0> Rmaxsigma ;
    real<lower=0> wtsigma ;
    real<lower=0> ksigma ;
    real<lower=0> psigma ;
    real<lower=0> qsigma ;
    real<lower=0> nu ;
  }
  model {
    Zmu ~ normal( 40 , 20 ) ;
    Rmaxmu ~ normal( 0.5 , 0.3 ) ;
    wtmu ~ normal( 1 , 0.5 ) ;
    kmu ~ normal( 0.2 , 0.05 ) ;
    pmu ~ normal( 0.4 , 0.2 ) ;
    qmu ~ normal( 2 , 0.5 ) ;
    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Zsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Rmaxsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    wtsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    ksigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    psigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    qsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    nu ~ exponential(1/30.0) ;
    Z ~ normal( Zmu , Zsigma ) ; // vectorized
    Rmax ~ normal( Rmaxmu , Rmaxsigma ) ; // vectorized
    wt ~ normal( wtmu , wtsigma ) ; // vectorized
    k ~ normal( kmu , ksigma ) ; // vectorized
    p ~ normal( pmu, psigma ) ;
    q ~ normal( qmu, qsigma ) ;
    for ( i in 1:Ntotal ) {

    if (c[i]==1)  // monocular condition
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])))) ,
                w[i]*sigma ) ;

     else if (c[i]==2)  // binocular condition 
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*((pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))) + (pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))))),
                w[i]*sigma ) ;

     else if (c[i]==3)  // dichoptic condition
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*((pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(48,q[s[i]]))) + (pow(48,p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(48,q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))))),
                w[i]*sigma ) ;

     else if (c[i]==4)  // binocular cross condition 
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]])))) ,
                w[i]*sigma ) ;

     else if (c[i]==5)  // dichoptic cross condition
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(48,q[s[i]])))) ,
                w[i]*sigma ) ;       
    }
  }

@@

      allmasksP[s,,] <- cleanmasksP  #/cleanmasksP[2,5]
      allmeansP[s,,] <- cleanmeansP  #/cleanmeansP[2,5]
      allmasksP2[s,,] <- cleanmasksP2  #/cleanmasksP2[2,5]
      allmeansP2[s,,] <- cleanmeansP2  #/cleanmeansP2[2,5]

@@

    # 1st harmonic
    condlist <- c(1,2,3,5,6)
    contlist <- c(6,12,24,48,96)
    y <- NULL
    x <- NULL
    c <- NULL
    s <- NULL
    w <- NULL
    i <- 0
    for (subj in 1:dim(allmeansP)[1]){
      for (cond in 1:length(condlist)){
        for (cont in 1:length(contlist)){
          dp <- abs(allmeansP[subj,condlist[cond],cont])
          if (includedvalues[expt,subj,condlist[cond],cont]==1){
            if (is.na(dp)==0){
              if (is.infinite(dp)==0){
                i <- i + 1
                x[i] <- contlist[cont]
                y[i] <- dp
                c[i] <- cond
                s[i] <- subj
                w[i] <- 1
              }
            }
          }
        }
      }
    }

    pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))

@@

    # 2nd harmonic
    condlist <- c(1,2,3,5,6)
    contlist <- c(6,12,24,48,96)
    y <- NULL
    x <- NULL
    c <- NULL
    s <- NULL
    w <- NULL
    i <- 0
    for (subj in 1:dim(allmeansP2)[1]){
      for (cond in 1:length(condlist)){
        for (cont in 1:length(contlist)){
          dp <- abs(allmeansP2[subj,condlist[cond],cont])
          if (includedvalues2[expt,subj,condlist[cond],cont]==1){
            if (is.na(dp)==0){
            if (is.infinite(dp)==0){
              i <- i + 1
              x[i] <- contlist[cont]
              y[i] <- dp
              c[i] <- cond
              s[i] <- subj
              w[i] <- 1
            }
          }
          }
          }
      }
    }

    pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))

@@

# create figure containing modelling results

@@

  nchains <- dim(pupilsamples)[2]
  pupilweightpopLum <- NULL
  pupilZpopLum <- NULL
  pupilKpopLum <- NULL
  pupilPpopLum <- NULL
  pupilQpopLum <- NULL
  pupilRpopLum <- NULL

  for (n in 1:nchains){
    pupilweightpopLum <- c(pupilweightpopLum,pupilsamples@sim$samples[[n]]$wtmu)
    pupilZpopLum <- c(pupilZpopLum,pupilsamples@sim$samples[[n]]$Zmu)
    pupilKpopLum <- c(pupilKpopLum,pupilsamples@sim$samples[[n]]$kmu)
    pupilPpopLum <- c(pupilPpopLum,pupilsamples@sim$samples[[n]]$pmu)
    pupilQpopLum <- c(pupilQpopLum,pupilsamples@sim$samples[[n]]$qmu)
    pupilRpopLum <- c(pupilRpopLum,pupilsamples@sim$samples[[n]]$Rmaxmu)
  }

  pupilWLum <- 10^(map_estimate(log10(pupilweightpopLum)))
  pupilZLum <- 10^(map_estimate(log10(pupilZpopLum)))
  pupilKLum <- 10^(map_estimate(log10(pupilKpopLum)))/sqrt(24)
  pupilPLum <- 10^(map_estimate(log10(pupilPpopLum+pupilQpopLum)))
  pupilQLum <- 10^(map_estimate(log10(pupilQpopLum)))
  pupilRmaxLum <- 10^(map_estimate(log10(pupilRpopLum)))

@@

  nchains <- dim(pupilsamples)[2]
  pupilweightpopMel <- NULL
  pupilZpopMel <- NULL
  pupilKpopMel <- NULL
  pupilPpopMel <- NULL
  pupilQpopMel <- NULL
  pupilRpopMel <- NULL

  for (n in 1:nchains){
    pupilweightpopMel <- c(pupilweightpopMel,pupilsamples@sim$samples[[n]]$wtmu)
    pupilZpopMel <- c(pupilZpopMel,pupilsamples@sim$samples[[n]]$Zmu)
    pupilKpopMel <- c(pupilKpopMel,pupilsamples@sim$samples[[n]]$kmu)
    pupilPpopMel <- c(pupilPpopMel,pupilsamples@sim$samples[[n]]$pmu)
    pupilQpopMel <- c(pupilQpopMel,pupilsamples@sim$samples[[n]]$qmu)
    pupilRpopMel <- c(pupilRpopMel,pupilsamples@sim$samples[[n]]$Rmaxmu)
  }

  pupilWMel <- 10^(map_estimate(log10(pupilweightpopMel)))
  pupilZMel <- 10^(map_estimate(log10(pupilZpopMel)))
  pupilKMel <- 10^(map_estimate(log10(pupilKpopMel)))/sqrt(24)
  pupilPMel <- 10^(map_estimate(log10(pupilPpopMel+pupilQpopMel)))
  pupilQMel <- 10^(map_estimate(log10(pupilQpopMel)))
  pupilRmaxMel <- 10^(map_estimate(log10(pupilRpopMel)))

@@

  nchains <- dim(pupilsamples)[2]
  pupilweightpopLM <- NULL
  pupilZpopLM <- NULL
  pupilKpopLM <- NULL
  pupilPpopLM <- NULL
  pupilQpopLM <- NULL
  pupilRpopLM <- NULL

  for (n in 1:nchains){
    pupilweightpopLM <- c(pupilweightpopLM,pupilsamples@sim$samples[[n]]$wtmu)
    pupilZpopLM <- c(pupilZpopLM,pupilsamples@sim$samples[[n]]$Zmu)
    pupilKpopLM <- c(pupilKpopLM,pupilsamples@sim$samples[[n]]$kmu)
    pupilPpopLM <- c(pupilPpopLM,pupilsamples@sim$samples[[n]]$pmu)
    pupilQpopLM <- c(pupilQpopLM,pupilsamples@sim$samples[[n]]$qmu)
    pupilRpopLM <- c(pupilRpopLM,pupilsamples@sim$samples[[n]]$Rmaxmu)
  }

  pupilWLM <- 10^(map_estimate(log10(pupilweightpopLM)))
  pupilZLM <- 10^(map_estimate(log10(pupilZpopLM)))
  pupilKLM <- 10^(map_estimate(log10(pupilKpopLM)))/sqrt(24)
  pupilPLM <- 10^(map_estimate(log10(pupilPpopLM+pupilQpopLM)))
  pupilQLM <- 10^(map_estimate(log10(pupilQpopLM)))
  pupilRmaxLM <- 10^(map_estimate(log10(pupilRpopLM)))

@@

  nchains <- dim(pupilsamples)[2]
  pupilweightpopS <- NULL
  pupilZpopS <- NULL
  pupilKpopS <- NULL
  pupilPpopS <- NULL
  pupilQpopS <- NULL
  pupilRpopS <- NULL

  for (n in 1:nchains){
    pupilweightpopS <- c(pupilweightpopS,pupilsamples@sim$samples[[n]]$wtmu)
    pupilZpopS <- c(pupilZpopS,pupilsamples@sim$samples[[n]]$Zmu)
    pupilKpopS <- c(pupilKpopS,pupilsamples@sim$samples[[n]]$kmu)
    pupilPpopS <- c(pupilPpopS,pupilsamples@sim$samples[[n]]$pmu)
    pupilQpopS <- c(pupilQpopS,pupilsamples@sim$samples[[n]]$qmu)
    pupilRpopS <- c(pupilRpopS,pupilsamples@sim$samples[[n]]$Rmaxmu)
  }

  pupilWS <- 10^(map_estimate(log10(pupilweightpopS)))
  pupilZS <- 10^(map_estimate(log10(pupilZpopS)))
  pupilKS <- 10^(map_estimate(log10(pupilKpopS)))/sqrt(24)
  pupilPS <- 10^(map_estimate(log10(pupilPpopS+pupilQpopS)))
  pupilQS <- 10^(map_estimate(log10(pupilQpopS)))
  pupilRmaxS <- 10^(map_estimate(log10(pupilRpopS)))

@@

  nchains <- dim(pupilsamples2)[2]
  pupilweightpopLum2 <- NULL
  pupilZpopLum2 <- NULL
  pupilKpopLum2 <- NULL
  pupilPpopLum2 <- NULL
  pupilQpopLum2 <- NULL
  pupilRpopLum2 <- NULL

  for (n in 1:nchains){
    pupilweightpopLum2 <- c(pupilweightpopLum2,pupilsamples2@sim$samples[[n]]$wtmu)
    pupilZpopLum2 <- c(pupilZpopLum2,pupilsamples2@sim$samples[[n]]$Zmu)
    pupilKpopLum2 <- c(pupilKpopLum2,pupilsamples2@sim$samples[[n]]$kmu)
    pupilPpopLum2 <- c(pupilPpopLum2,pupilsamples2@sim$samples[[n]]$pmu)
    pupilQpopLum2 <- c(pupilQpopLum2,pupilsamples2@sim$samples[[n]]$qmu)
    pupilRpopLum2 <- c(pupilRpopLum2,pupilsamples2@sim$samples[[n]]$Rmaxmu)
  }

  pupilWLum2 <- 10^(map_estimate(log10(pupilweightpopLum2)))
  pupilZLum2 <- 10^(map_estimate(log10(pupilZpopLum2)))
  pupilKLum2 <- 10^(map_estimate(log10(pupilKpopLum2)))/sqrt(24)
  pupilPLum2 <- 10^(map_estimate(log10(pupilPpopLum2+pupilQpopLum2)))
  pupilQLum2 <- 10^(map_estimate(log10(pupilQpopLum2)))
  pupilRmaxLum2 <- 10^(map_estimate(log10(pupilRpopLum2)))

@@

  nchains <- dim(pupilsamples2)[2]
  pupilweightpopMel2 <- NULL
  pupilZpopMel2 <- NULL
  pupilKpopMel2 <- NULL
  pupilPpopMel2 <- NULL
  pupilQpopMel2 <- NULL
  pupilRpopMel2 <- NULL

>>>>

---
title: 'Binocular combination in the autonomic nervous system'
author: |
 | Federico G. Segala$^1$, Joel T. Martin$^{1,2}$, Annie Y. Morsi$^1$, Alex R. Wade$^{1,3}$ & Daniel H. Baker$^{1,3}$
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: true
  html_document: default
bibliography: references.bib
link-citations: yes
linkcolor: black
csl: elife.csl
header-includes:
- \usepackage{caption}
---

@@

processdata <- 1  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 56GB of storage)

@@

# cut off for data inclusion (Mahalanobis distance for complex data)
SDthresh <<- 3
nbootstraps <<- 10000

@@

# settings for sampler 
numSavedSteps <- 100000    # total number of MCMC steps
adaptSteps <- 1000  # Number of steps to "tune" the samplers
burnInSteps <- 2000 
thinSteps <- 10
nChains <- 16
ncores <- 8
options(mc.cores=ncores)

@@

$^2$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, United Kingdom.

$^3$York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.

@@

  includedvalues <- array(0,dim=c(4,24,6,5))
  includedvalues2 <- array(0,dim=c(4,24,6,5))
  includedmasks <- array(0,dim=c(4,24,6,5))
  includedmasks2 <- array(0,dim=c(4,24,6,5))

@@

      temp <- tempmasksP[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        includedmasks[expt,i,cond,level] <- 1
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmasksP[cond,level] <- mean(temp[i])
        cleanmasksPCI[1,cond,level] <- mbs$lowerCI
        cleanmasksPCI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmeansP2[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        includedvalues2[expt,i,cond,level] <- 1
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmeansP2[cond,level] <- mean(temp[i])
        cleanmeansP2CI[1,cond,level] <- mbs$lowerCI
        cleanmeansP2CI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmasksP2[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        includedmasks2[expt,i,cond,level] <- 1
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmasksP2[cond,level] <- mean(temp[i])
        cleanmasksP2CI[1,cond,level] <- mbs$lowerCI
        cleanmasksP2CI[2,cond,level] <- mbs$upperCI
      }
    }
  }

@@

  save(file=paste0(datadir,'included.RData'),list=c('includedvalues','includedvalues2','includedmasks','includedmasks2'))

@@

CRFmodelstring = "
  data {
    int<lower=1> Nsubj ;
    int<lower=1> Ntotal ;
    real y[Ntotal] ;
    real x[Ntotal] ;
    int<lower=1> c[Ntotal] ;
    int<lower=1> s[Ntotal] ;
  }
  parameters {
    real<lower=1> Z[Nsubj] ;
    real<lower=0> Rmax[Nsubj] ;
    real<lower=0> wt[Nsubj] ;
    real<lower=0> k[Nsubj] ;
    real<lower=0> p[Nsubj] ;    
    real<lower=0> q[Nsubj] ;    
    real<lower=0> sigma ;
    real<lower=1> Zmu ; 
    real<lower=0> Rmaxmu ; 
    real<lower=0> wtmu ; 
    real<lower=0> kmu ; 
    real<lower=0> pmu ;     
    real<lower=0> qmu ;     
    real<lower=0> Zsigma ;
    real<lower=0> Rmaxsigma ;
    real<lower=0> wtsigma ;
    real<lower=0> ksigma ;
    real<lower=0> psigma ;
    real<lower=0> qsigma ;
    real<lower=0> nu ;
  }
  model {
    Zmu ~ normal( 40 , 20 ) ;
    Rmaxmu ~ normal( 0.5 , 0.3 ) ;
    wtmu ~ normal( 1 , 0.5 ) ;
    kmu ~ normal( 0.002 , 0.001 ) ;
    pmu ~ normal( 0.4 , 0.2 ) ;
    qmu ~ normal( 2 , 0.5 ) ;
    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Zsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Rmaxsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    wtsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    ksigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    psigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    qsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    nu ~ exponential(1/30.0) ;
    Z ~ normal( Zmu , Zsigma ) ; // vectorized
    Rmax ~ normal( Rmaxmu , Rmaxsigma ) ; // vectorized
    wt ~ normal( wtmu , wtsigma ) ; // vectorized
    k ~ normal( kmu , ksigma ) ; // vectorized
    p ~ normal( pmu, psigma ) ;
    q ~ normal( qmu, qsigma ) ;
    for ( i in 1:Ntotal ) {

    if (c[i]==1)  // monocular condition F1
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])))) ,
                sigma ) ;

     else if (c[i]==2)  // binocular condition F1
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*((pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))) + (pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))))),
                sigma ) ;

     else if (c[i]==3)  // dichoptic condition F1
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*((pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(48,q[s[i]]))) + (pow(48,p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(48,q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))))),
                sigma ) ;

     else if (c[i]==4)  // binocular cross condition F1
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]])))) ,
                sigma ) ;

     else if (c[i]==5)  // dichoptic cross condition F1
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(48,q[s[i]])))) ,
                sigma ) ;

     else if (c[i]==6)  // monocular condition F2
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])))) ,
                sigma ) ;

     else if (c[i]==7)  // binocular cross condition F2
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]])))) ,
                sigma ) ;

     else if (c[i]==8)  // dichoptic cross condition F2
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*(pow(48,p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(48,q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]])))) ,
                sigma ) ;

    }
  }

@@

      allmasksP[s,,] <- cleanmasksP
      allmeansP[s,,] <- cleanmeansP
      allmasksP2[s,,] <- cleanmasksP2
      allmeansP2[s,,] <- cleanmeansP2

@@

    # 1st harmonic F1
    condlist <- c(1,2,3,5,6)
    contlist <- c(6,12,24,48,96)
    y <- NULL
    x <- NULL
    c <- NULL
    s <- NULL
    i <- 0
    for (subj in 1:dim(allmeansP)[1]){
      for (cond in 1:length(condlist)){
        for (cont in 1:length(contlist)){
          dp <- abs(allmeansP[subj,condlist[cond],cont])
          if (includedvalues[expt,subj,condlist[cond],cont]==1){
            if (is.na(dp)==0){
              if (is.infinite(dp)==0){
                i <- i + 1
                x[i] <- contlist[cont]
                y[i] <- dp
                c[i] <- cond
                s[i] <- subj
              }
            }
          }
        }
      }
    }
    # 1st harmonic F2
    condlist <- c(4,5,6)
    for (subj in 1:dim(allmasksP)[1]){
      for (cond in 1:length(condlist)){
        for (cont in 1:length(contlist)){
          dp <- abs(allmasksP[subj,condlist[cond],cont])
          if (includedmasks[expt,subj,condlist[cond],cont]==1){
            if (is.na(dp)==0){
              if (is.infinite(dp)==0){
                i <- i + 1
                x[i] <- contlist[cont]
                y[i] <- dp
                c[i] <- cond+5
                s[i] <- subj
              }
            }
          }
        }
      }
    }

    pupildatalist = list(x = x, y = y, s = s, c = c, Nsubj = max(s), Ntotal = length(y))

@@

    # 2nd harmonic
    condlist <- c(1,2,3,5,6)
    contlist <- c(6,12,24,48,96)
    y <- NULL
    x <- NULL
    c <- NULL
    s <- NULL
    i <- 0
    for (subj in 1:dim(allmeansP2)[1]){
      for (cond in 1:length(condlist)){
        for (cont in 1:length(contlist)){
          dp <- abs(allmeansP2[subj,condlist[cond],cont])
          if (includedvalues2[expt,subj,condlist[cond],cont]==1){
            if (is.na(dp)==0){
              if (is.infinite(dp)==0){
                i <- i + 1
                x[i] <- contlist[cont]
                y[i] <- dp
                c[i] <- cond
                s[i] <- subj
              }
            }
          }
        }
      }
    }
    # 2nd harmonic F2
    condlist <- c(4,5,6)
    for (subj in 1:dim(allmasksP)[1]){
      for (cond in 1:length(condlist)){
        for (cont in 1:length(contlist)){
          dp <- abs(allmasksP2[subj,condlist[cond],cont])
          if (includedmasks2[expt,subj,condlist[cond],cont]==1){
            if (is.na(dp)==0){
              if (is.infinite(dp)==0){
                i <- i + 1
                x[i] <- contlist[cont]
                y[i] <- dp
                c[i] <- cond+5
                s[i] <- subj
              }
            }
          }
        }
      }
    }

    pupildatalist = list(x = x, y = y, s = s, c = c, Nsubj = max(s), Ntotal = length(y))

@@

# get predictions of the model based on earlier fits

@@

  draws <- extract(pupilsamples)

  pupilweightpopLum <- draws$wtmu
  pupilZpopLum <- draws$Zmu
  pupilKpopLum <- draws$kmu
  pupilPpopLum <- draws$pmu
  pupilQpopLum <- draws$qmu
  pupilRpopLum <- draws$Rmaxmu

  pupilWLum <- 10^as.numeric(map_estimate(log10(pupilweightpopLum)))
  pupilZLum <- 10^as.numeric(map_estimate(log10(pupilZpopLum)))
  pupilKLum <- 10^as.numeric(map_estimate(log10(pupilKpopLum)))/sqrt(24)
  pupilPLum <- 10^as.numeric(map_estimate(log10(pupilPpopLum+pupilQpopLum)))
  pupilQLum <- 10^as.numeric(map_estimate(log10(pupilQpopLum)))
  pupilRmaxLum <- 10^as.numeric(map_estimate(log10(pupilRpopLum)))

@@

  draws <- extract(pupilsamples)

  pupilweightpopMel <- draws$wtmu
  pupilZpopMel <- draws$Zmu
  pupilKpopMel <- draws$kmu
  pupilPpopMel <- draws$pmu
  pupilQpopMel <- draws$qmu
  pupilRpopMel <- draws$Rmaxmu

  pupilWMel <- 10^as.numeric(map_estimate(log10(pupilweightpopMel)))
  pupilZMel <- 10^as.numeric(map_estimate(log10(pupilZpopMel)))
  pupilKMel <- 10^as.numeric(map_estimate(log10(pupilKpopMel)))/sqrt(24)
  pupilPMel <- 10^as.numeric(map_estimate(log10(pupilPpopMel+pupilQpopMel)))
  pupilQMel <- 10^as.numeric(map_estimate(log10(pupilQpopMel)))
  pupilRmaxMel <- 10^as.numeric(map_estimate(log10(pupilRpopMel)))

@@

  draws <- extract(pupilsamples)

  pupilweightpopLM <- draws$wtmu
  pupilZpopLM <- draws$Zmu
  pupilKpopLM <- draws$kmu
  pupilPpopLM <- draws$pmu
  pupilQpopLM <- draws$qmu
  pupilRpopLM <- draws$Rmaxmu

  pupilWLM <- 10^as.numeric(map_estimate(log10(pupilweightpopLM)))
  pupilZLM <- 10^as.numeric(map_estimate(log10(pupilZpopLM)))
  pupilKLM <- 10^as.numeric(map_estimate(log10(pupilKpopLM)))/sqrt(24)
  pupilPLM <- 10^as.numeric(map_estimate(log10(pupilPpopLM+pupilQpopLM)))
  pupilQLM <- 10^as.numeric(map_estimate(log10(pupilQpopLM)))
  pupilRmaxLM <- 10^as.numeric(map_estimate(log10(pupilRpopLM)))

@@

  draws <- extract(pupilsamples)

  pupilweightpopS <- draws$wtmu
  pupilZpopS <- draws$Zmu
  pupilKpopS <- draws$kmu
  pupilPpopS <- draws$pmu
  pupilQpopS <- draws$qmu
  pupilRpopS <- draws$Rmaxmu

  pupilWS <- 10^as.numeric(map_estimate(log10(pupilweightpopS)))
  pupilZS <- 10^as.numeric(map_estimate(log10(pupilZpopS)))
  pupilKS <- 10^as.numeric(map_estimate(log10(pupilKpopS)))/sqrt(24)
  pupilPS <- 10^as.numeric(map_estimate(log10(pupilPpopS+pupilQpopS)))
  pupilQS <- 10^as.numeric(map_estimate(log10(pupilQpopS)))
  pupilRmaxS <- 10^as.numeric(map_estimate(log10(pupilRpopS)))

@@

  draws <- extract(pupilsamples2)

  pupilweightpopLum2 <- draws$wtmu
  pupilZpopLum2 <- draws$Zmu
  pupilKpopLum2 <- draws$kmu
  pupilPpopLum2 <- draws$pmu
  pupilQpopLum2 <- draws$qmu
  pupilRpopLum2 <- draws$Rmaxmu

  pupilWLum2 <- 10^as.numeric(map_estimate(log10(pupilweightpopLum2)))
  pupilZLum2 <- 10^as.numeric(map_estimate(log10(pupilZpopLum2)))
  pupilKLum2 <- 10^as.numeric(map_estimate(log10(pupilKpopLum2)))/sqrt(24)
  pupilPLum2 <- 10^as.numeric(map_estimate(log10(pupilPpopLum2+pupilQpopLum2)))
  pupilQLum2 <- 10^as.numeric(map_estimate(log10(pupilQpopLum2)))
  pupilRmaxLum2 <- 10^as.numeric(map_estimate(log10(pupilRpopLum2)))

@@

  draws <- extract(pupilsamples2)

  pupilweightpopMel2 <- draws$wtmu
  pupilZpopMel2 <- draws$Zmu
  pupilKpopMel2 <- draws$kmu
  pupilPpopMel2 <- draws$pmu
  pupilQpopMel2 <- draws$qmu
  pupilRpopMel2 <- draws$Rmaxmu
